---
title: "Rworksheet_Ulgasan#4c"
output: pdf_document
date: "2023-11-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Use the dataset mpg
• Download and open the mpg file. Upload it to your OWN environment
a. Show your solutions on how to import a csv file into the environment.


```{r}


library(readr)
mpg <- read_csv("rWorksheet_ulgasan4a/Worksheet_4c/mpg.csv")
mpg
View(mpg)
```
b. Which variables from mpg dataset are categorical?
```{r}




mpg <- read.csv('rWorksheet_ulgasan4a/Worksheet_4c/mpg.csv')

head(mpg)

str(mpg)

```
c. Which are continuous variables?

```{r}


str(mpg$displ)
str(mpg$year)
str(mpg$cyl)
str(mpg$trans)
str(mpg$drv)
str(mpg$cty)
str(mpg$hwy)


```
2. Which manufacturer has the most models in this data set? Which model has the most variations?
Show your answer
```{r}


data(mpg)


manufacturer_table <- table(mpg$manufacturer)


max_manufacturer <- as.character(names(manufacturer_table)[which.max(manufacturer_table)])
print(paste("The manufacturer with the most models is '", max_manufacturer, "'."))


model_table <- table(mpg$model)
max_model <- as.character(names(model_table)[which.max(model_table)])
print(paste("The model with the most variations is '", max_model, "'."))


```
2a. Group the manufacturers and find the unique models. Show your codes and result.
```{r}

data(mpg)


grouped_models <- aggregate(mpg$model, by=list(manufacturer=mpg$manufacturer), unique)
print(grouped_models)

View(grouped_models)
```
2b. Graph the result by using plot() and ggplot(). Write the codes and its result
```{r}




df <- data.frame(vehicle_type = c("car", "car", "truck", "truck"),
                 hwy = c(30, 35, 25, 27),
                 cty = c(18, 20, 15, 17))


df$mpg <- ifelse(df$vehicle_type == "car", 
                 (df$cty + df$hwy) / 2, 
                 df$hwy)


library(ggplot2)

ggplot(df, aes(x = vehicle_type, y = mpg, fill = vehicle_type)) +
 geom_bar(stat = "identity", position = "dodge") +
 labs(title = "Miles per Gallon (mpg) for Cars and Trucks",
       x = "Vehicle Type",
       y = "Miles per Gallon (mpg)") +
 theme_minimal()



```
2.Same dataset will be used. You are going to show the relationship of the modeland the manufacturer.

```{r}


library(ggplot2)


ggplot(mpg, aes(x = manufacturer, y = model)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Relationship between Model and Manufacturer",
       x = "Manufacturer",
       y = "Model")



```
2a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?


```{r}

#X-axis (horizontal): Car models.
#Y-axis (vertical): Car manufacturers.
#Points: Each point on the plot represents a specific car model and its corresponding manufacturer in the mpg dataset.


#This plot provides a visual representation of how different car models are distributed across various manufacturers. Each point on the plot indicates a pairing of a specific car model with its manufacturer. It's a way to explore the relationships and patterns in the data. If there are a lot of points, you might see overlapping, and adjusting the plot (for example, using jitter or other techniques) could enhance readability.

```
2b. For you, is it useful? If not, how could you modify the data to make it more informative?
```{r}

ggplot(mpg, aes(x = model, y = manufacturer, color = fl)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Relationship between Model, Manufacturer, and Fuel Type",
       x = "Model",
       y = "Manufacturer")


```

3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and
its results.

```{r}



library(ggplot2)


ggplot(head(mpg, 20), aes(x = model, y = year)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(title = "Relationship between Model and Year (Top 20 Observations)",
       x = "Model",
       y = "Year")
 

```
4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result


```{r}

library(dplyr)

car_counts <- mpg %>%
  group_by(model) %>%
  summarize(number_of_cars = n())

print(car_counts)



```
4a. Plot using geom_bar() using the top 20 observations only. The graphs shoudl have a title, labels and
colors. Show code and results.

```{r}

top_20 <- head(mpg, 20)


barplot(table(top_20$model),
        main = "Number of Cars per Model (Top 20 Observations)",
        xlab = "Model",
        ylab = "Number of Cars",
        col = rainbow(length(unique(top_20$model))))

legend("topright", legend = levels(factor(top_20$model)), fill = rainbow(length(unique(top_20$model))))



```
4b. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.
```{r}


library(ggplot2)


ggplot(head(mpg, 20), aes(x = model)) +
  geom_bar() +
  coord_flip() +
  labs(title = "Number of Cars per Model (Top 20 Observations)",
       x = "Model",
       y = "Number of Cars")
      


```
5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using
geom_point with aesthetic color = engine displacement. Title should be “Relationship between
No. of Cylinders and Engine Displacement”.

```{r}



library(ggplot2)


ggplot(mpg, aes(x = cyl, y = displ, color = displ)) +
  geom_point() +
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders",
       y = "Engine Displacement")

```

5a. How would you describe its relationship? Show the codes and its result

```{r}


summary(mpg[c("cyl", "displ")])


cor(mpg$cyl, mpg$displ)

plot(mpg$cyl, mpg$displ, main = "Scatter Plot: Cylinders vs. Engine Displacement",
     xlab = "Number of Cylinders", ylab = "Engine Displacement")
abline(lm(displ ~ cyl, data = mpg), col = "red")



```
6. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped
it with a continuous variable you have identified in #1-c. What is its result? Why it produced such
output?


```{r}


library(ggplot2)


ggplot(mpg, aes(x = displ, y = hwy, color = cyl)) +
  geom_point() +
  labs(title = "Relationship between Engine Displacement and Highway MPG",
       x = "Engine Displacement",
       y = "Highway MPG")


```

6. Import the traffic.csv onto your R environment.

```{r}





```
6.b

```{r}


```
6.c
```{r}




```
7b.From alexa_file.xlsx, import it to your environment

```{r}




```



