---
title: "Rworksheet_Ulgasan#4c"
output: pdf_document
date: "2023-11-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Use the dataset mpg
• Download and open the mpg file. Upload it to your OWN environment
a. Show your solutions on how to import a csv file into the environment.


```{r}


library(readr)
mpg <- read_csv("rWorksheet_ulgasan4a/Worksheet_4c/mpg.csv")
mpg
View(mpg)
```
b. Which variables from mpg dataset are categorical?
```{r}




mpg <- read.csv('rWorksheet_ulgasan4a/Worksheet_4c/mpg.csv')

head(mpg)

str(mpg)

```
c. Which are continuous variables?

```{r}


str(mpg$displ)
str(mpg$year)
str(mpg$cyl)
str(mpg$trans)
str(mpg$drv)
str(mpg$cty)
str(mpg$hwy)


```
2. Which manufacturer has the most models in this data set? Which model has the most variations?
Show your answer
```{r}


data(mpg)


manufacturer_table <- table(mpg$manufacturer)


max_manufacturer <- as.character(names(manufacturer_table)[which.max(manufacturer_table)])
print(paste("The manufacturer with the most models is '", max_manufacturer, "'."))


model_table <- table(mpg$model)
max_model <- as.character(names(model_table)[which.max(model_table)])
print(paste("The model with the most variations is '", max_model, "'."))


```
2a. Group the manufacturers and find the unique models. Show your codes and result.
```{r}

data(mpg)


grouped_models <- aggregate(mpg$model, by=list(manufacturer=mpg$manufacturer), unique)
print(grouped_models)


```
2b. Graph the result by using plot() and ggplot(). Write the codes and its result
```{r}

manufacturer_counts <- table(grouped_models$manufacturer)
manufacturer_proportions <- manufacturer_counts / sum(manufacturer_counts)


pie(manufacturer_proportions, labels=names(manufacturer_proportions), main="Proportion of Unique Models by Manufacturer")




```


