---
title: "RWorksheet_Ulgasan#4b"
output:
  pdf_document: default
date: "2023-11-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1.Using the for loop, create an R script that will display a 5x5 matrix as shown in
Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.

```{r name, echo = TRUE}


vectorA <- c(1, 2, 3, 4, 5)
matrixA <- matrix(0, nrow = 5, ncol = 5)

cat("Initial Matrix:\n")
print(matrixA)
for (i in 1:5) {
  matrixA[i, ] <- vectorA * i
}


cat("\nFinal Matrix:\n")
matrixA


```
2.2. Print the string "*" using for() function. The output should be the same as shown
in Figure


```{r name, echo = TRUE}



for(i in 1:5){
  asterisk <- rep("*", i)
  print(asterisk)
  
}


```

3.Get an input from the user to print the Fibonacci sequence starting from the 1st input up to 500. Use repeat and break statements. Write the R Scripts and its output.

```{r name, echo = TRUE}

fibonacci <- function(n) {
 if (n <= 1)
    return(n)
 else
    return(fibonacci(n-1) + fibonacci(n-2))
}


cat("Enter a number: ")
input <- readLines(n=1)


input_num <- as.numeric(input)


if (is.na(input_num)) {
 cat("Invalid input. Please enter a valid number.")
} else {

 cat("Fibonacci sequence: \n")
 i <- 1
 while (i <= 500) {
    if (i < input_num) {
      i <- i + 1
    } else {
      cat(fibonacci(i), "\n")
      i <- i + 1
     break 
    }
 }
}



```

4.a What is the R script for importing an excel or a csv file? Display the first 6 rows of
the dataset? Show your codes and its result

```{r name, echo = TRUE}
lastData <- read.csv("householdData.csv")
head(lastData)
getwd()


```

4.b Create a subset for gender(female and male). How many observations are there in
Male? How about in Female? Write the R scripts and its output.
```{r name, echo = TRUE}



male_data <- subset(data, gender == "Male")
female_data <- subset(data, gender == "Female")


nrow(male_data)
nrow(female_data)


data <- data.frame(name = c("Alice", "Bob", "Cathy", "David", "Eva"),
                   gender = c("Female", "Male", "Female", "Male", "Female"),
                   age = c(25, 30, 35, 40, 45))


male_data <- subset(data, gender == "Male")
female_data <- subset(data, gender == "Female")

 
nrow(male_data)
nrow(female_data)

```
4.e Create a graph for the number of males and females for Household Data. Use plot(),
chart type = barplot. Make sure to place title, legends, and colors. Write the R scripts and
its result.
```{r name, echo = TRUE}

totalMaleFemale <-table(lastData$Gender)

barplot(totalMaleFemale,
        main = "number of males and females",
        xlab = "gender",
        ylab = "count",
        col = c("red", "black"),
        legend.text = rownames(totalMaleFemale),
        beside = TRUE)
     


```
5.a Create a piechart that will include labels in percentage.Add some colors and title of
the chart. Write the R scripts and show its output.


```{r name, echo = TRUE}



install.packages("plotrix")
library(plotrix)


food <- 60
electricity <- 10
savings <- 5
miscellaneous <- 25


total_income <- food + electricity + savings + miscellaneous


labels <- c("Food", "Electricity", "Savings", "Miscellaneous")
sizes <- c(food, electricity, savings, miscellaneous)

pie3D.labels(sizes, labels, clockwise = TRUE, 
             col = rainbow(length(labels)),
             main = "Dela Cruz Family Income Distribution")


percentages <- round((sizes / total_income) * 100, 1)


data.frame(Category = labels, Percentage = percentages)


```
6a. Check for the structure of the dataset using the str() function. Describe what you
have seen in the output.

```{r name, echo = TRUE}
str(iris)

#Information about iris blossoms is gathered in the iris dataset. It contains measurements for 150 distinct iris flowers, including the length and width of the petals, which are two more parts of the flower, and the sepals, which are a portion of the flower. It also notes the specific species of iris to which each flower belongs. The dataset contains three species: virgnica, versicolor, and setosa.


```

6b. Create an R object that will contain the mean of the sepal.length,
sepal.width,petal.length,and petal.width. What is the R script and its result?
```{r name, echo = TRUE}

meanOfiris <-colMeans(iris[,1:4])
meanOfiris



```

6c. Create a pie chart for the Species distribution. Add title, legends, and colors. Write
the R script and its result.
```{r name, echo = TRUE}
speciesOfiris <- table(iris$Species)
speciesOfiris
nameOfSpecies <- c("Setosa", "Versicolor","Vriginica")
nameOfSpecies

pie(speciesOfiris,
   labels = speciesOfiris,
   col = c("red","yellow","blue"),
   main = "Species Distribution in Iris Dataset")
    
legend("topright",
       legend = levels(iris$Species),
       fill = c("red","yellow","blue"),)




```
6d. Subset the species into setosa, versicolor, and virginica. Write the R scripts
and show the last six (6) rows of each species.
```{r name, echo = TRUE}
subSetosa <- subset(iris, Species =="setosa")

subVer<- subset(iris,Species == "versicolor")

subVirg <- subset(iris,Species == "virginica")

tail(subSetosa)
tail(subVer)
tail(subVirg)


```
6e. Create a scatterplot of the sepal.length and sepal.width using the different
species(setosa,versicolor,virginica). Add a title = “Iris Dataset”, subtitle = “Sepal
width and length, labels for the x and y axis, the pch symbol and colors should be based on
the species.
```{r name, echo = TRUE}
plot(iris$Sepal.Length,
iris$Sepal.Width,
xlab = "Sepal Length",
main = "Iris Dataset", sub = "Sepal width and length",
pch = as.numeric(iris$Species),
col = as.numeric(iris$Species))


legend("topright", 
levels(iris$Species),
pch = 1:4,
col = 1:4,
title = "Species")


```

7a. Rename the white and black variants by using gsub() function.

```{r name, echo = TRUE}
library(readxl)


alexa_file <- read_excel("alexa_file.xlsx")
View(alexa_file)
alexa_file




alexa_file$variation <- gsub("Black  Dot", "BlackDot", alexa_file$variation)
alexa_file$variation <- gsub("Black  Plus", "BlackPlus", alexa_file$variation)
alexa_file$variation <- gsub("Black  Show", "BlackShow", alexa_file$variation)
alexa_file$variation <- gsub("White  Plus", "WhitePlus", alexa_file$variation)


alexa_file$variation <- gsub("White  Show", "WhiteShow", alexa_file$variation)
alexa_file$variation <- gsub("White  Spot", "WhiteSpot", alexa_file$variation)
View(alexa_file)
alexa_file
```
7.bGet the total number of each variations and save it into another object. Save the
object as variations.RData. Write the R scripts. What is its result?

```{r name, echo = TRUE}



# Load required library
library(dplyr)

#
variation_counts <- df %>%
  group_by(variation) %>%
  summarise(count = n())

save(variation_counts, file = "variations.RData")


print(variation_counts)


load("variations.RData")



```
7c. From the variations.RData, create a barplot(). Complete the details of the chart
which include the title, color, labels of each bar.
```{r name, echo = TRUE}
barplot(variation_counts$count, 
        names.arg = variation_counts$variation,
        col = "skyblue",
        main = "Variation Counts",
        xlab = "Variation",
        ylab = "Count")

# Add labels
text(x = barplot(variation_counts$count, 
                 names.arg = variation_counts$variation,
                 col = "skyblue", 
                 main = "Variation Counts",
                 xlab = "Variation",
                 ylab = "Count", 
                 ylim = c(0, max(variation_counts$count) + 1),
                 space = 0.3), 
     y = variation_counts$count, 
     label = variation_counts$count, 
     pos = 3, 
     col = "black")

# Add a legend
legend("topright", legend = "Count", fill = "skyblue", border = NA)



```
7d. Create a barplot() for the black and white variations. Plot it in 1 frame, side by
side. Complete the details of the chart.


```{r name, echo = TRUE}


library(ggplot2)

{r}
par(mfrow = c(1,2))
black <- data.frame(
 variation = c("black", "black plus", " black show","black spot ", "black dot" ),
 n = c(261, 270, 265, 241, 516)
)


barplot_black <- ggplot(black, aes(x = variation, y = n, fill = variation)) +
 geom_bar(stat = "identity", position = "dodge") +
 geom_text(aes(label = n), position = position_dodge(width = 0.5), vjust = -0.9) +
 scale_fill_manual(values = c("black", "pink","green","blue", "skyblue")) +
 theme_minimal() +
 labs(title = "Black Variations", x = "Variation", y = "Count")


white <- data.frame(
  variation = c("white", "white dot", "white plus", "white show", "white spot"),
  n = c(261, 516, 231, 261,320 )
)

barplot_white <- ggplot(white, aes(x = variation, y = n, fill = variation)) +
 geom_bar(stat = "identity", position = "dodge") +
 geom_text(aes(label = n), position = position_dodge(width = 0.5), vjust = -0.9) +
 scale_fill_manual(values = c("black", "pink","green","blue", "skyblue")) +
 theme_minimal() +
 labs(title = "White Variations", x = "Variation", y = "Count")
  
  barplot_white
  barplot_black

```

